---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mypackage

<!-- badges: start -->
[![R-CMD-check](https://github.com/ESMerrall/mypackage/workflows/R-CMD-check/badge.svg)](https://github.com/ESMerrall/mypackage/actions)
<!-- badges: end -->

The goal of mypackage is to print a personalised greeting from me!

## Installation

You can install the released version of mypackage from Github with:

``` r
devtools::install_github("ESMerrall/mypackage")
```

## Example

This is a basic example which shows you how to print a generic greeting:

```{r example}
library(mypackage)
## basic example code
hello()
```

This is a basic example which shows you how to print a personalised greeting:

```{r}
hello(name="Lottie Locks")
```


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
